---
title: "Example"
output: html_document
---
Before performing this Example code, please run the **Functions.R** file firstly.

# Show properties of different similarity graphs

I create this dataset which contains two data areas. These two data regions are created to have different density for investigating the performance of different similarity graphs.

The similarity_graph $S$ are built by Gaussian similarity function with sigma being 1. The $k$ parameter of mutual k-near ann k-near graphs is 10; the $\epsilon$ of $\epsilon$-neighborhood graph is 0.02.


```{r,echo = false}
# Load required library
library(mixtools)
library(MASS)
library(corpcor)
library(conclust)
```



```{r,results='hide'}

norm_2dim = mvrnorm(n = 50, mu = c(0,-1), Sigma = diag(0.15,2), tol = 1e-6, empirical = FALSE, EISPACK = FALSE)
mid_moon = matrix(ncol = 2,nrow = 50)
for (i in 1:50) {
  mid_moon[i,1]  =runif(1,min = 0,max = 1.5)
  mid_moon[i,2] = (mid_moon[i,1]-0.75)^2 - rnorm(1,mean = -0.05,sd = 0.1)
}
data_2dim = rbind(mid_moon,norm_2dim)

mutual_k_near = 10
k_near = 10
par(mfrow=c(2,2))
Similarity_graph = Build_similarity_graph(data_2dim)
plot(data_2dim,main = paste("Two dimensional data"),ylab = "",xlab = "")
# Epsilon graph
epsilon = 0.02
W_matrix = Build_W(Similarity_graph = Similarity_graph,epsilon =  epsilon)
plot(data_2dim,main = paste("Epsilon graph, epsilon =",epsilon,sep = ""),ylab = "",xlab = "")
for (i in 1:nrow(data_2dim)) {
  for (j in 1:nrow(data_2dim)) {
    if(W_matrix[i,j]!=1 && W_matrix[i,j]!=0){
      par(new=TRUE)
      lines(data_2dim[c(i,j),],col = 4)
    }
  }
}


Similarity_graph = Build_similarity_graph(data_2dim)
# K-nearest graph
W_matrix = Build_W(Similarity_graph = Similarity_graph,k_near = k_near)
plot(data_2dim,main = paste("K-nearest graph, k =",k_near,sep = ""),ylab = "",xlab = "")
for (i in 1:nrow(data_2dim)) {
  for (j in 1:nrow(data_2dim)) {
    if(W_matrix[i,j]!=1 && W_matrix[i,j]!=0){
      par(new=TRUE)
      lines(data_2dim[c(i,j),],col = 4)
    }
  }
}

# Mutual K-nearest graph
W_matrix = Build_W(Similarity_graph = Similarity_graph,mutual_k_near = mutual_k_near)
plot(data_2dim,main = paste("Mutual K-nearest graph, k =",mutual_k_near,sep = ""),ylab = "",xlab = "")
for (i in 1:nrow(data_2dim)) {
  for (j in 1:nrow(data_2dim)) {
    if(W_matrix[i,j]!=1 && W_matrix[i,j]!=0){
      par(new=TRUE)
      lines(data_2dim[c(i,j),],col = 4)
    }
  }
}
```

# Perform the spectral clustering using a toy example

Simulate the dataset from a mixture of two Gaussians.

We can control the standard deviation of this Multivariate Gaussian mixture model by changing the sigma matrix. The higher the standard deviation, the closer these two data areas.

```{r,results='hide'}
library(mixtools)
library(MASS)
library(corpcor)

set.seed(1)
n = 200
lambda = rep(1, 2)/2
mu = matrix(c(1,4,8,12),ncol = 2, nrow = 2)
sigma = matrix(0.6,2,2)
data_2dim_sd0.5 = rmvnormmix(n, lambda, mu, sigma)
data_2dim_sd0.5 = data_2dim_sd0.5[order(data_2dim_sd0.5[,1],decreasing = FALSE),]
plot(data_2dim_sd0.5,main = paste("Two dimensional data; sd 0.5"),ylab = "",xlab = "")

set.seed(1)
sigma = matrix(1.5,2,2)
data_2dim_sd1.5 = rmvnormmix(n, lambda, mu, sigma)
data_2dim_sd1.5 = data_2dim_sd1.5[order(data_2dim_sd1.5[,1],decreasing = FALSE),]
plot(data_2dim_sd1.5,main = paste("Two dimensional data; sd 1.5"),ylab = "",xlab = "")
```

Unnormalized graph laplacian using dataset with standard deviation 0.5

```{r,results='hide'}
par(mfrow=c(2,2))
test = Spectral_clustering(data = data_2dim_sd0.5,sigma = 1,k_near=10, mutual_k_near = NULL,epsilon = NULL, Full_graph = FALSE,Graph_laplacian = "Unnormalized",Number_of_cluster = 2)
plot(rev(test$eigen_values)[1:10],main = "The smallest 10 eigenvalues",ylab = "Value",xlab = "The smallest k eigenvalue")
plot(test$selected_vectors[,2],type = "l",main = "The first eigenvector of eigenvalue 0",xlab = "The kth coordinate",ylab = "")
plot(test$selected_vectors[,1],type = "l",main = "The second eigenvector of eigenvalue 0",xlab = "The kth coordinate",ylab = "")

```

Unnormalized graph laplacian using dataset with standard deviation 1.5

```{r,results='hide'}
par(mfrow=c(2,2))
test = Spectral_clustering(data = data_2dim_sd1.5,sigma = 1,k_near=10, mutual_k_near = NULL,epsilon = NULL, Full_graph = FALSE,Graph_laplacian = "Unnormalized",Number_of_cluster = 2)
plot(rev(test$eigen_values)[1:10],main = "The smallest 10 eigenvalues",ylab = "Value",xlab = "The smallest k eigenvalue")
plot(test$selected_vectors[,2],type = "l",main = "The first eigenvector of eigenvalue 0",xlab = "The kth coordinate",ylab = "")
plot(test$selected_vectors[,1],type = "l",main = "The second eigenvector of eigenvalue 0",xlab = "The kth coordinate",ylab = "")

```

Unnormalized graph laplacian using dataset with standard deviation 1.5, using four eigenvectors

You can use more eigenvectors by changing the parameter value of **more**


```{r,results='hide'}
par(mfrow=c(2,2))
test = Spectral_clustering_moreeigenvectors(data = data_2dim_sd1.5,sigma = 1,more = 2,k_near=10, mutual_k_near = NULL,epsilon = NULL, Full_graph = FALSE,Graph_laplacian = "Unnormalized",Number_of_cluster = 2)
plot(rev(test$eigen_values)[1:10],main = "The smallest 10 eigenvalues",ylab = "Value",xlab = "The smallest k eigenvalue")
plot(test$selected_vectors[,2],type = "l",main = "The first eigenvector of eigenvalue 0",xlab = "The kth coordinate",ylab = "")
plot(test$selected_vectors[,1],type = "l",main = "The second eigenvector of eigenvalue 0",xlab = "The kth coordinate",ylab = "")

```



Normalized graph laplacian using dataset with standard deviation 1.5

```{r,results='hide'}
par(mfrow=c(2,2))
test = Spectral_clustering(data = data_2dim_sd1.5,sigma = 1,k_near=10, mutual_k_near = NULL,epsilon = NULL, Full_graph = FALSE,Graph_laplacian = "Normalized_rw",Number_of_cluster = 2)
plot(rev(test$eigen_values)[1:10],main = "The smallest 10 eigenvalues",ylab = "Value",xlab = "The smallest k eigenvalue")
plot(test$selected_vectors[,2],type = "l",main = "The first eigenvector of eigenvalue 0",xlab = "The kth coordinate",ylab = "")
plot(test$selected_vectors[,1],type = "l",main = "The second eigenvector of eigenvalue 0",xlab = "The kth coordinate",ylab = "")


```




